The K2 Bright Star Survey

### 2019-05-06 paper/ms.tex
okina

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
% added by DH
\usepackage{xspace}
\usepackage{amsmath}

@@

\author[0000-0001-8832-4488 ]{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

Unlike other methods for calibrating \kepler systematics, other than the value of $l$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm. The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise.

@@

In order to choose the objective function $\Lambda_{k,l}$, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the halo sample and one with very little high frequency variability detected or predicted, which was also observed at short cadence. We choose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better. We calculate halo lightcurves and their CDPPs for $k \in \{1,2,3\}$, and $l \in [1,50]$ for long cadence and (sparsely) $l \in [1,2500]$ for short cadence data. The results are displayed in Figure~\ref{cdpps}. We find that for long cadence data, the L1 norm (TV) and a lag of 10 provide the best CDPP, which is unsurprising given that this is a slightly shorter lag than the 12~cadence thruster firing period. In this context we can understand the optimum as TV-min suppressing systematics on the same timescale as they occur. On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ and improves very slowly with $l$ for longer lags, and performs very poorly for $k=3$ at all lags.

@@

@@

In addition to these changes in objective function, we have also added a feature `\texttt{deathstar}' to deal with contamination. We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out. \textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion. We now iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.

>>>>

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
% added by DH
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{newunicodechar,graphicx}

\DeclareRobustCommand{\okina}{%
  \raisebox{\dimexpr\fontcharht\font`A-\height}{%
    \scalebox{0.8}{`}%
  }%
}
\newunicodechar{ʻ}{\okina}

@@

\author[0000-0001-8832-4488 ]{Daniel Huber}
\affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

@@

In order to choose the values for $k$ and $l$ in our objective function, we have selected the quiet star 36~Ophiuchi, the lowest-mass main sequence star in the halo sample and one with very little high frequency variability detected or predicted, which was also observed at short cadence. We choose the 6.5~hour Combined Differential Photometric Precision \citep[CDPP,][]{cdpp} as implemented in \texttt{lightkurve} \citep{lightkurve} as a proxy for the `noise' in a lightcurve, with lower being better. We calculate halo lightcurves and their CDPPs for $k \in \{1,2,3\}$, and $l \in [1,50]$ for long cadence and (sparsely) $l \in [1,2500]$ for short cadence data. The results are displayed in Figure~\ref{cdpps}. We find that for long cadence data, the L1 norm (TV) and a lag of 10 provide the best CDPP, which is unsurprising given that this is a slightly shorter lag than the 12~cadence thruster firing period. In this context we can understand the optimum as TV-min suppressing systematics on the same timescale as they occur. On the other hand, for short cadence data, performance at short lags is very poor but the method performs similarly for $k \in \{1,2\}$ and improves very slowly with $l$ for longer lags, and performs very poorly for $k=3$ at all lags.

@@

%  improvements
Unlike other methods for calibrating \kepler systematics, other than the value of $l$, no knowledge of the spacecraft motion or the behaviour of an ensemble of other stars is used to inform our algorithm. The method is a self-calibration that is independent of the details of the systematics it is calibrating, operating on the assumption that a single signal is present across many individual time series which otherwise are contaminated by noise. It is therefore likely that significant improvements can be made to the method by including cotrending basis vectors with mean zero and whose weights are allowed to be negative, which would represent systematics which are common to all pixels in the halo aperture and therefore masquerade as signal. Any linear combination of convex objective functions is itself convex, and future extensions to the method could enforce combinations of different lags and orders to better represent systematics occurring on different timescales (e.g. thruster firings, red noise) and with different levels of smoothness.

@@

In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination. We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out. \textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion. We now iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.
